Template for GTEx example on cluster

### 2017-10-05 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

---
title: "Template for GTEx example on cluster"
author: "wei"
date: 09-29
output: html_document
---

@@

```
load("~/flash/dataanalysis/GTeX/EQTLzscore/gtexEQTL_zscore.rds")
setwd("~/flash/dataanalysis/GTeX/EQTLzscore/")
source("./sfawrapper.R")
source("./SFAmixwrapper.R")
Y = zscore
N = dim(Y)[1]
P = dim(Y)[2]
gsfa = SFA.wrapper(Y, 26)
saveRDS(gsfa, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfaGTExzscore.rds")

gsfamix = SFAmix.wrapper(Y,30)
saveRDS(gsfamix, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfamixGTExzscore.rds")

@@

SFA provide NaN result when set `K = 30` and `K = 26`. (all the $L_i$ and $F_j$ are NaN).

>>>>

---
title: "Template for GTEx example on cluster"
author: "wei"
date: 09-29
output: 
  html_document:
    code_folding: hide
---

@@

```
load("~/flash/dataanalysis/GTeX/EQTLzscore/gtexEQTL_zscore.rds")
setwd("~/flash/dataanalysis/GTeX/EQTLzscore/")
source("./sfawrapper.R")
source("./SFAmixwrapper.R")
Y = zscore
N = dim(Y)[1]
P = dim(Y)[2]
gsfa = SFA.wrapper(Y, 30)
saveRDS(gsfa, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfaGTExzscore.rds")

Y = t(zscore)
gsfamix = SFAmix.wrapper(Y,30)
saveRDS(gsfamix, file = "~/flash/dataanalysis/GTeX/EQTLzscore/sfamixGTExzscore.rds")

@@

#### remark

For `Y = t(zscore)`, SFA provide NaN result when set `K = 30` and `K = 26`. (all the $L_i$ and $F_j$ are NaN). So I use `Y = zscore` which works in `K = 30` and `K = 26`. In this case, I set `K = 30`

in this case we can get

```
> gsfa = SFA.wrapper(Y, 30)
 Setting G to be 16069
 Setting N to be 44
Trying to read in matrix with G=16069 and N =44
Opening matrix ./dscsfa.txt with 16069 rows and 44 columns
Opening matrix ./dscsfa.txt with 16069 rows and 44 columns
read in matrix 16069 by 44
initializing sfa...
G = 16069
N = 44
K = 30

But for `SFAmix` we should use `Y = t(zscore)`.

The approaches make sure we can get $(\hat{\sigma}_1^2,\cdots,\hat{\sigma}_j^2,\cdots)$ is a `16069` vector.

### plot SFA result

```{r}
sfares = readRDS("../data/GTExdata/SFAres/sfaGTExzscore.rds")
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:30){
  barplot(sfares$F[,k],main = paste("factor",k))
}
